Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-26 Moltres.tex
inches to cm

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units.

@@

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
chosen to correspond to the peak of the thermal flux in both cases; for the
\gls{ORNL} calculations this is 8.4 inches from the core center-line because of
the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
higher z-values than the Moltres lines. Additionally, absorption
in the plena cause deviation of the thermal flux from a sinusoidal shape in the
\gls{MSRE} design case.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial.eps}
    \caption{Moltres axial flux profiles along core center line and \gls{MSRE}
      design axial flux profiles 8.4 inches from core center line \cite[p. 91]{briggs_molten-salt_1964}.}
    \label{fig:axial_fluxes_compare}
\end{figure}

>>>>

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations on a single 
mesh in anywhere from one to three dimensions and can be deployed on an 
arbitrary number of processing units.

@@

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
chosen to correspond to the peak of the thermal flux in both cases; for the
\gls{ORNL} calculations this is 21.336 cm (8.4 inches) from the core center-line because of
the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
higher z-values than the Moltres lines. Additionally, absorption
in the plena cause deviation of the thermal flux from a sinusoidal shape in the
\gls{MSRE} design case.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial.eps}
    \caption{Moltres axial flux profiles along the core center line and \gls{MSRE}
    design axial flux profiles 21.336 cm (8.4 inches) from the core center line \cite[p. 91]{briggs_molten-salt_1964}.}
    \label{fig:axial_fluxes_compare}
\end{figure}

### 2017-11-26 revise/revise.tex
inches to cm

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
\begin{solution}
        <++>
\end{solution}

@@

\question The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?
\begin{solution}
        <++>
\end{solution}

>>>>

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
\begin{solution}
        This has now been clarified in the introductory text. The equations are 
        solved on a single mesh. This is enabled by the underlying MOOSE 
        framework, which also enables 'loose' coupling instead.
\end{solution}

@@

\question The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?
\begin{solution}
        These calculations were performed without including turbulence. However, a $k-\epsilon$ model is being implemented to support future simulations.
\end{solution}
